---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Lesbarkeitsindex Flesh

```{r}
library(ggplot2)

tab <- read.table("./output/text-analysis-all.csv", header=TRUE, sep=",")

ggplot(tab, aes(x=flesh, y = words, shape = factor(selected), color=factor(selected))) + 
  geom_point(na.rm=TRUE, size=1) + #, alpha = 0.2
  facet_grid(document ~ .) +
  labs(title="Lesbarkeit", x="Flesh Lesbarkeitsindex", y='Worte pro Satz') +
  theme_bw() +
    theme(panel.background = element_rect(colour = "white", linetype = "dashed")) +
    theme(legend.key = element_rect(colour = "white", size=1)) +
    theme(legend.key.size = unit(4, "mm")) +
    theme(legend.position="bottom") +
    theme(panel.border = element_rect(colour = "white")) +
    theme(strip.background = element_rect(colour = "white", fill = "white", size = 0)) +
    theme(strip.text.x = element_text(colour = "black", angle = 90, size = 9, hjust = .5, vjust = 0)) +
    theme(axis.ticks.x = element_line(colour="white")) +
    theme(axis.text.y = element_text(colour = "black", size = 9)) +
    theme(axis.text.x = element_text(colour = "white", size = 0))

#print(plot)


```

bla

```{r}
library(ggplot2)



for (id in c(1,2,3,4,5,6,7)){
  tab <- read.table(paste0("text-analysis-ke",id,".csv"), header=TRUE, sep=",")
  plot <- ggplot(tab, aes(x=flesh, y = words)) + 
    geom_point(na.rm=TRUE) +
    labs(title=paste0("Kurseinheit ",id), x="Flesh Index", y='Words per sentence')
  print(plot)
}


```


Audio-Länge

```{r}

library(ggplot2)

d <- read.table('../output/duration.csv', header=TRUE, sep=",")

aggregate(d$duration, list(d$ke), sd)

plot <- ggplot(d, aes(y=duration, x = voice)) + 
  geom_bar(stat="identity") +
  facet_grid(. ~ ke) +
  labs(title='', x="Stimmen", y='Dauer (s)')+
    theme_bw() +
    theme(panel.background = element_rect(colour = "white", linetype = "dashed")) +
   # theme(legend.key = element_rect(colour = "white", size=1)) +
    #theme(legend.key.size = unit(4, "mm")) +
    theme(legend.position="bottom") +
    theme(panel.border = element_rect(colour = "white")) +
    theme(strip.background = element_rect(colour = "white", fill = "white", size = 0)) +
    theme(strip.text.x = element_text(colour = "black", angle = 0, size = 9, hjust = .5, vjust = 0)) +
    theme(axis.ticks.x = element_line(colour="white")) +
    theme(axis.text.y = element_text(colour = "black", size = 9))+
theme(axis.text.x = element_text(colour = "black", size = 9, angle=90)) 
 
print(plot) 

ggsave(file="/home/abb/Documents/proj_008-LLP/img/duration.pdf", plot=plot, width=10, height=8)


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
